---
title       : Mtcars Analysis
subtitle    : linear model for mpg
author      : shawn huang
job         : Engineer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## Overview
### Purpose

provide an interactive approach to build up linear model for mpg in mtcars

### Procedure

* select the variables in the sidebar panel.
* click linear model tab in the main panel.
* check the output of the linear model in the main panel.

--- .class #id 

## Datasets 

```{r echo = FALSE,results='hide'}
names <- names(mtcars)
agg.names<-paste0(names,collapse =",")
```

The variables in the mtcars dataset are `r agg.names`  
This following is the first 10 rows in mtcars

```{r echo = FALSE}
head(mtcars,10)
```

---

## Select variable

We will use the variables showing in the sidebar to build up the linear model for mpg.  
Please select the variables in the sidebar.  

<img class=center src=./fig/sidebar.png height=500>

---

## Linear model
```{r echo = FALSE,results='hide'} 
mt.vars <- paste(names(mtcars)[-1], collapse=",")
```

* Select the variables from the sidebar . ex: `r mt.vars`
* Show the linear model result in the main panel
<img class=center src=./fig/main.png height=500>
